TODO

### 2021-05-24 paper2/sec-schemechange.tex

For the additional power in $\alpha$ we therefore have a mismatch between the evolution equations and the collinear counter term in the fixed-order calculation.
We can correct for this mismatch by introducing a new term in the fixed-order calculation, which is the difference between the collinear counter term with a running $\overline{\mathrm{MS}}$ $\alpha (\mu)$, and the counter term actually used.
If we assume for the following that we use a $G_\mu$ input scheme for $\alpha$, this term is the collinear counter term, with the additional power in $\alpha$ replaced by
\begin{equation}
\alpha (Q^2) - \alpha_{G_\mu} \text{,} \label{eq:consistency-condition}
\end{equation}
and the remaining powers of $\alpha$ in the LO matrix element as chosen in the fixed-order calculation.
Consistency requires this term not to introduce additional singularities at NLO EW, so we have to expand $\alpha (Q^2)$, at the order given by the evolution equations used for fitting the PDFs.
For example, in leading-logarithmic approximation,
\begin{equation}
\alpha (Q^2) = \frac{\alpha (\mu^2)}{1 - \alpha (\mu^2)/(3\pi) \ln (Q^2/\mu^2)} \text{,}
\end{equation}
we can find a scale $\mu^2$ so that $\alpha (\mu^2) = \alpha_{G_\mu}$, and therefore eq.~\eqref{eq:consistency-condition} becomes
\begin{equation}
\alpha (Q^2) - \alpha_{G_\mu} = \frac{\alpha_{G_\mu}^2}{3 \pi} \ln \frac{Q^2}{\mu^2} + \mathcal{O} (\alpha_{G_\mu}^3) \text{,}
\end{equation}
which shows that although there is a non-trivial consistency condition at NLO EW, the difference is formally higher order.

>>>>

For the additional power in $\alpha$ we therefore have a mismatch between the evolution equations and the collinear counter term in the fixed-order calculation.
We can correct for this mismatch by introducing a new term in the fixed-order calculation, which is the difference between the collinear counter term with a running $\overline{\mathrm{MS}}$ $\hat{\alpha} (\mu_\mathrm{R})$, and the counter term actually used.
If we assume for the following that we use a $G_\mu$ input scheme for $\alpha$, this term is the collinear counter term, with the additional power in $\alpha$ replaced by the difference of $\alpha_{G_\mu}$ and the $\overline{\text{MS}}$ coupling $\hat{\alpha} (\mu_\mathrm{R}^2)$:
\begin{equation}
\hat{\alpha} (\mu_\mathrm{R}^2) - \alpha_{G_\mu} = \alpha_{G_\mu} \left( \Delta \hat{\alpha} (\mu_\mathrm{R}^2) - \Delta r^{(1)} + \ldots \right) \text{,} \label{eq:consistency-condition}
\end{equation}
which uses the following definitions,
\begin{equation}
\hat{\alpha} (\mu_\mathrm{R}^2) = \frac{\alpha(0)}{1 - \Delta \hat{\alpha} (\mu_\mathrm{R}^2)} \text{,} \qquad \alpha_{G_\mu} = \alpha(0) \left( 1 + \Delta r^{(1)} \right) + \mathcal{O} (\alpha(0)^3) \text{,}
\end{equation}
which in make use of the fine-structure constant $\alpha(0)$; all quantities are given e.g.\ in ref.~\cite{Denner:2019vbn} and references therein.
Since all $\Delta$ terms are $\mathcal{O} (\alpha)$, the difference in eq.~\eqref{eq:consistency-condition} is $\mathcal{O} (\alpha^2)$ and therefore zero at NLO EW in the full perturbative calculation.
This must be the case, otherwise the scheme-change operator we defined above would introduce additional singularities.
